---
title: "Main results"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preperations

```{r}
rm(list = ls())
gc()
library(ggplot2)
library(ggpubr)
library(here)
library(vroom)
library(data.table)
library(dplyr)
source(here("src/research/def_data_prep.R"))

here()
```

```{r}
LOAD_AGGR_DATA = TRUE
PATH <- here::here("data_output/exp")
```


## Aggregate on model level

```{r}
if (!LOAD_AGGR_DATA){
  # load data
  df <- arrow::open_dataset(PATH)

  df_model_list <- c()
  n_models = 5600
  steps = 10
  step_size <- n_models / steps
  
  # process the data in smaller chunks
  for (i in 1:steps) {
    i <- i - 1
    lb <- i * step_size
    ub <- i * step_size + step_size
    print(c(i, lb, ub))
      
    df_model_list[[i+1]] <- df |>
        
        # filter by model index to process only a subset of models
        filter(model_index >= lb & model_index < ub) |>
        
        # transform some variables
        mutate(
         Prioritization = contact_tracing_population_sort_mode,
         ever_infected = ifelse(ever_infected == T, 1, 0),
         ever_icu = ifelse(!is.na(date_icu), 1, 0)
       ) |>
      
        # group by agent (one agent exists in every (50) replication of a model)
        group_by(
         Prioritization,
         contact_tracing_frac,
         model_index,
         unique_agent_id
       ) |>
      
       # average on agent level
       summarize(
         ever_infected = mean(ever_infected),
         ever_icu = mean(ever_icu),
         n_times_contact_tracing = mean(n_times_contact_tracing),
         n_contacts_traced = mean(n_contacts_traced)
       ) |>
      
      # group by model
      group_by(
         Prioritization,
         contact_tracing_frac,
         model_index,
       ) |>
      
       # count infections etc. per model
       summarize(
         n_infected = sum(ever_infected),
         n_icu = sum(ever_icu),
         n_times_contact_tracing = sum(n_times_contact_tracing),
         n_contacts_traced = sum(n_contacts_traced)
       ) |>
       collect()
  }
  
  df <- do.call(rbind, df_model_list)
  
  df$Prioritization <- factor(
      x=df$Prioritization,
      levels=c(
        "random",
        "super-spreaders",
        "household_size",
        "age",
        "inc_rank_sim",
        "inc_rank_emp",
        "young",
        "old"
        ),
      labels=c(
        "1. Random", 
        "2. HH+Age", 
        "3. HH", 
        "4. Age",  
        "5. Inc. sim.", 
        "6. Inc. emp.",  
        "7. Young", 
        "8 .Old")
    )

  df <- df[!is.na(df$Prioritization),]
}
```

```{r}
if (!LOAD_AGGR_DATA){
  df_ori <- df
  saveRDS(df_ori, file=paste(PATH, "df_aggr.rdata", sep="/"))
}
```

```{r}
if (LOAD_AGGR_DATA){
  df <- readRDS(here::here("data_output/exp/df_aggr.rdata"))
  df_ori <- df
}

```

## Calculate main effect measures

```{r}
df <- df_ori
df <- as.data.table(df)
```

```{r}
# calculate number of prevented infections
n_infected_baseline<- mean(df[contact_tracing_frac==0, n_infected])
df$n_infections_prevented <- n_infected_baseline - df$n_infected
df$share_infections_prevented <- df$n_infections_prevented / n_infected_baseline
df$ppt <- df$n_infections_prevented / (df$n_times_contact_tracing + df$n_contacts_traced)
df$ppt[is.infinite(df$ppt)] <- 0 # set the ppt to 0 if the denominator is 0 (baseline scenarios)

# calculate number of prevented icu
n_icu_baseline<- mean(df[contact_tracing_frac==0, n_icu])
df$n_icu_prevented <- n_icu_baseline - df$n_icu
df$share_icu_prevented <- df$n_icu_prevented / n_icu_baseline
df$ppt_icu <- df$n_icu_prevented / (df$n_times_contact_tracing + df$n_contacts_traced)
df$ppt_icu[is.infinite(df$ppt_icu)] <- 0 # set the ppt to 0 if the denominator is 0 (baseline scenarios)
```


## Eval replications

```{r}
df <- as.data.frame(df)

counter <- 1
dfs <- c()
for (prio in unique(df$Prioritization)){
  for (ctf in unique(df$contact_tracing_frac)){
    df_temp <- get_replications(df[df$Prioritization == prio & df$contact_tracing_frac == ctf,], mean, "n_infections_prevented")
    df_temp$Prioritization <- prio
    df_temp$contact_tracing_frac <- ctf
    dfs[[counter]] <- df_temp
    counter <- counter + 1
  }
}

df_mean <- do.call(rbind, dfs)

plots <- list()
counter <- 1
for (ctf in sort(unique(df_mean$contact_tracing_frac))){
  (
    g <- ggplot(data=df_mean[df_mean$contact_tracing_frac == ctf,], mapping=aes(x=n, y=estimate, color=Prioritization))
    + geom_point()
    + geom_line()
    #+ ylim(0, 1200)
    + xlab("Number of models (with 50 replications)")
    + ylab("Average number of prevented infections")
    + ggtitle(paste("Share of prioritized agents = ", as.character(ctf), sep=""))
    + theme(plot.title = element_text(hjust = 0.5))
  )
  if (ctf > 0){
    plots[[counter]] <- g
    counter <- counter + 1
  }
}
g <- ggarrange(plotlist=plots, ncol = 2, nrow = 3, common.legend=TRUE, legend="bottom")
ggsave(here(paste("img/fig_reps_infections.pdf", sep="")), width=12, height=16)
ggsave(here(paste("img/fig_reps_infections.png", sep="")), width=12, height=16)
g
```

```{r}
df <- as.data.frame(df)

counter <- 1
dfs <- c()
for (prio in unique(df$Prioritization)){
  for (ctf in unique(df$contact_tracing_frac)){
    df_temp <- get_replications(df[df$Prioritization == prio & df$contact_tracing_frac == ctf,], mean, "ppt")
    df_temp$Prioritization <- prio
    df_temp$contact_tracing_frac <- ctf
    dfs[[counter]] <- df_temp
    counter <- counter + 1
  }
}

df_mean <- do.call(rbind, dfs)

plots <- list()
counter <- 1
for (ctf in sort(unique(df_mean$contact_tracing_frac))){
  
  (
    g <- ggplot(data=df_mean[df_mean$contact_tracing_frac == ctf,], mapping=aes(x=n, y=estimate, color=Prioritization))
    + geom_point()
    + geom_line()
    #+ ylim(0, 1200)
    + xlab("Number of models (with 50 replications)")
    + ylab("Average number of prevented infections per tracing")
    + ggtitle(paste("Experiments: Share of prioritized agents = ", as.character(ctf), sep=""))
    + theme(plot.title = element_text(hjust = 0.5))
  )
  if (ctf > 0){
    plots[[counter]] <- g
    counter <- counter + 1
  }
}

g <- ggarrange(plotlist=plots, ncol = 2, nrow = 3, common.legend=TRUE, legend="bottom")
ggsave(here(paste("img/fig_reps_ppt.pdf", sep="")), width=12, height=16)
ggsave(here(paste("img/fig_reps_ppt.png", sep="")), width=12, height=16)
g
```


## Aggregate per scenario

```{r}
# average by scenario
df_aggr <- aggregate(
 x=list(
   "n_infected"=df$n_infected,
   "n_icu"=df$n_icu,
   "n_times_contact_tracing"=df$n_times_contact_tracing,
   "n_infections_prevented"=df$n_infections_prevented,
   "share_infections_prevented"=df$share_infections_prevented,
   "ppt"=df$ppt,
   "n_icu_prevented"=df$n_icu_prevented,
   "share_icu_prevented"=df$share_icu_prevented,
   "ppt_icu"=df$ppt_icu
   ),
 by=list(
   "Prioritization"=df$Prioritization, 
   "contact_tracing_frac"=df$contact_tracing_frac
   ),
 FUN=mean
)

df_aggr[is.na(df_aggr$ppt), "ppt"] <- 0
df_aggr[is.na(df_aggr$ppt_icu), "ppt_icu"] <- 0

# remove scenarios with 0 contact tracing
df_no_zero_frac <- df[df$contact_tracing_frac>0,]
```


# Results

```{r}
add_space <- function(){theme(plot.margin = unit(c(1,1,1,1), 'lines'))}
xlabel <- function(){xlab("Share of prioritized agents")}
axis_font_size <- function(){theme(axis.text = element_text(size = 8), axis.title = element_text(size = 9))}
rotate_x_labels <- function(){theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))}
xlabel_prio <- function(){xlab("Prioritization")}
whitespace_title <- function(){ggtitle(" ")}

dot_size_1 <- 0.1

WIDTH = 8
HEIGHT = 4
```


## Share of prevented infections (total)

```{r}
g_mean_prinf <- (
  ggpubr::ggerrorplot(
    data=df_no_zero_frac,
    x="Prioritization",
    y="share_infections_prevented",
    color="Prioritization",
    desc_stat="mean_ci",
    size=dot_size_1,
    add.params = list(size = 0.1, alpha = 0.2)
  ) 
  + grids(linetype = "dashed")
  + theme_bw()
  + add_space()
  + axis_font_size()
  + theme(aspect.ratio=1)
  + rotate_x_labels()
  + xlabel_prio()
  + ylab("Share of prevented infections")
  + whitespace_title()
)

g_mean_prinf
```


```{r}
aggregate(
  df_no_zero_frac$share_infections_prevented,
  list(
    df_no_zero_frac$Prioritization
    ), FUN=mean)
```


## Prevented infections per share of prioritized agents

```{r}
g_prevented_infections <- (
  ggplot(
    data=df_aggr, 
    mapping=aes(
      x=contact_tracing_frac, 
      y=share_infections_prevented, 
      color=Prioritization
      )
    )
  + geom_line(data=df_aggr[df_aggr$Prioritization=="1. Random",], size=1.25)
  + geom_line(alpha=0.5, size=0.5)
  + geom_line(data=df_aggr[df_aggr$Prioritization=="1. Random",], width=2)
  
  + geom_point(alpha=0.8)
  + xlabel()
  + ylab("Share of prevented infections")
  + theme_bw()
  + add_space()
  + axis_font_size()
  + theme(plot.title = element_text(size=9, face="bold", hjust = 0.5))
  + theme(aspect.ratio=1)
  + whitespace_title()
)
g_prevented_infections
```

## Summary: Prevented infections

```{r}

ct_infections <- cowplot::plot_grid(
  g_mean_prinf + theme(legend.position = "none"),
  g_prevented_infections + theme(legend.position = "none"),
  align="vh",
  labels = c("A", "B"),
  nrow = 1
  )

ct_infections <- annotate_figure(
  ct_infections, 
  top = text_grob("Prevented infections", face = "bold", 
  size = 14),
  )
ggsave(here("img/fig_exp_infections.pdf"), width = WIDTH, height = HEIGHT, dpi = 300)
ggsave(here("img/fig_exp_infections.png"), width = WIDTH, height = HEIGHT, dpi = 300)
ct_infections
```



## Prevented infections per tracing (total)

```{r}
g_mean_ppt <- (
  ggpubr::ggerrorplot(
  data=df_no_zero_frac,
  x="Prioritization",
  y="ppt",
  color="Prioritization",
  desc_stat="mean_ci",
  size=dot_size_1,
  add.params = list(size = 0.1, alpha = 0.2),
  #add="jitter"
  ) 
  + grids(linetype = "dashed")
  + theme_bw()
  + add_space()
  + axis_font_size()
  + theme(aspect.ratio=1)
  + rotate_x_labels()
  + xlabel_prio()
  + ylab("Infections prevented per tracing")
  + axis_font_size()
  + theme(aspect.ratio=1)
  + rotate_x_labels()
  + whitespace_title()
  + theme(legend.position = "none")
)

g_mean_ppt
```
```{r}
aggregate(
  df_no_zero_frac$ppt,
  list(
    df_no_zero_frac$Prioritization
    ), FUN=mean)
```


## Prevented infections per tracing per share of prio. agents

```{r}
g_ppt_line <- (
  ggplot(
    data=df_aggr, 
    mapping=aes(
      x=contact_tracing_frac, 
      y=ppt, 
      color=Prioritization
      )
    )
  + geom_line(data=df_aggr[df_aggr$Prioritization=="1. Random",], size=1.25)
  + geom_line(alpha=0.5, size=0.5)
  + geom_point()
  + xlabel()
  + theme_bw()
  + add_space()
  + axis_font_size()
  + ylab("Infections prevented per tracing")
  + scale_color_discrete(name = "Prioritization")
  + theme(plot.title = element_text(size=9, face="bold", hjust = 0.5))
  + theme(aspect.ratio=1)
  + whitespace_title()
)
g_ppt_line
```


## Summary: Prevented infections per tracing

```{r}
ct_ppt <- cowplot::plot_grid(
  g_mean_ppt + theme(legend.position = "none"),
  g_ppt_line + theme(legend.position = "none"),
  align="vh",
  labels = c("A", "B"),
  nrow = 1
  )

ct_ppt <- annotate_figure(
  ct_ppt, 
  top = text_grob("Prevented infections per tracing", face = "bold", 
  size = 14),
  )
ggsave(here("img/fig_exp_ppt.pdf"), width = WIDTH, height = HEIGHT, dpi = 300)
ggsave(here("img/fig_exp_ppt.png"), width = WIDTH, height = HEIGHT, dpi = 300)
ct_ppt
```


## Share of prevented hospitalizations (total)

```{r}

g_mean_pricu <- (
  ggpubr::ggerrorplot(
    data=df_no_zero_frac,
    x="Prioritization",
    y="share_icu_prevented",
    color="Prioritization",
    desc_stat="mean_ci",
    size=dot_size_1,
    add.params = list(size = 0.1, alpha = 0.2)
  ) 
  + grids(linetype = "dashed")
  + theme_bw()
  + add_space()
  + axis_font_size()
  + theme(aspect.ratio=1)
  + rotate_x_labels()
  + xlabel_prio()
  + ylab("Share of prevented hospitalizations")
  + whitespace_title()
  + theme(legend.position = "none")
)

g_mean_pricu
```


## Prevented hospitalizations per tracing per share of prioritized agents

```{r}
g_prevented_icu <- (
  ggplot(
    data=df_aggr, 
    mapping=aes(
      x=contact_tracing_frac, 
      y=share_icu_prevented, 
      color=Prioritization
      )
    )
  + geom_line(data=df_aggr[df_aggr$Prioritization=="1. Random",], size=1.25)
  + geom_line(alpha=0.5, size=0.5)
  + geom_point(alpha=0.8)
  + xlabel()
  + ylab("Share of prevented hospitalizations")
  + theme_bw()
  + add_space()
  + axis_font_size()
  + theme(plot.title = element_text(size=9, face="bold", hjust = 0.5))
  + theme(aspect.ratio=1)
  + theme(legend.position = "none")
  + whitespace_title()
  )
g_prevented_icu
```


## Summary: Prevented hospitalizations

```{r}
ct_icu <- cowplot::plot_grid(
  g_mean_pricu + theme(legend.position = "none"),
  g_prevented_icu + theme(legend.position = "none"),
  align="vh",
  labels = c("A", "B"),
  nrow = 1
  )

ct_icu <- annotate_figure(
  ct_icu, 
  top = text_grob("Prevented hospitalizations", face = "bold", 
  size = 14),
  )
ggsave(here("img/fig_exp_icu.pdf"), width = WIDTH, height = HEIGHT, dpi = 300)
ggsave(here("img/fig_exp_icu.png"), width = WIDTH, height = HEIGHT, dpi = 300)
ct_icu
```


## Prevented hospitalizations per tracing (total)

```{r}
g_mean_ppt_icu <- (
  ggpubr::ggerrorplot(
  data=df_no_zero_frac,
  color="Prioritization",
  x="Prioritization",
  y="ppt_icu",
  desc_stat="mean_ci",
  size=dot_size_1,
  add.params = list(size = 0.1, alpha = 0.2),
  ) 
  + grids(linetype = "dashed")
  + theme_bw()
  + add_space()
  + axis_font_size()
  + theme(aspect.ratio=1)
  + rotate_x_labels()
  + xlabel_prio()
  + ylab("Hospitalizations prevented per tracing")
  + axis_font_size()
  + theme(aspect.ratio=1)
  + rotate_x_labels()
  + whitespace_title()
  + theme(legend.position = "none")
)

g_mean_ppt_icu

aggregate(df_no_zero_frac$ppt_icu, list(
  df_no_zero_frac$Prioritization
  ), FUN=mean)
```


## Prevented hospitalizations per tracing per share of prio. agents

```{r}
g_ppt_icu_line <- (
  ggplot(
    data=df_aggr,
    mapping=aes(
      x=contact_tracing_frac, 
      y=ppt_icu, 
      color=Prioritization
      )
    )
  + geom_line(data=df_aggr[df_aggr$Prioritization=="1. Random",], size=1.25)
  + geom_line(alpha=0.5, size=0.5)
  + geom_point(alpha=0.8)
  + xlabel()
  + theme_bw()
  + add_space()
  + axis_font_size()
  + ylab("Hospitalizations prevented per tracing")
  + scale_color_discrete(name = "Prioritization")
  + theme(plot.title = element_text(size=9, face="bold", hjust = 0.5))
  + theme(aspect.ratio=1)
  + theme(legend.position = "none")
  + whitespace_title()
)
g_ppt_icu_line
```

```{r}
ct_ppt_icu <- cowplot::plot_grid(
  g_mean_ppt_icu + theme(legend.position = "none"),
  g_ppt_icu_line + theme(legend.position = "none"),
  align="vh",
  labels = c("A", "B"),
  nrow = 1
  )

ct_ppt_icu <- annotate_figure(
  ct_ppt_icu, 
  top = text_grob("Prevented hospitalizations per tracing", face = "bold", 
  size = 14),
  )
ggsave(here("img/fig_exp_ppt_icu.pdf"), width = WIDTH, height = HEIGHT, dpi = 300)
ggsave(here("img/fig_exp_ppt_icu.png"), width = WIDTH, height = HEIGHT, dpi = 300)
ct_ppt_icu
```

